\bf Supplement to "Mechanistic models for panel data: analysis of ecological experiments with four interacting species"

### 2024-04-03 si/si.Rnw
Update

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[authoryear,numbers]{natbib}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyphenat}
\tolerance=1000
\usepackage{url}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage{hyphenat}
\usepackage{Sweave}
\bibliographystyle{apalike}
\newcommand{\blind}{0}

@@

\if1\blind
{
  \title{\bf Mechanistic models for panel data: analysis of ecological experiments with four interacting species}
  \author{Author 1\thanks{
    The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
    Department of YYY, University of XXX\\
    and \\
    Author 2 \\
    Department of ZZZ, University of WWW}
  \maketitle
} \fi

\if0\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Mechanistic models for panel data: analysis of ecological experiments with four interacting species}
\end{center}
  \medskip
} \fi

\bigskip
<<Setup, include=FALSE,echo=FALSE,results=hide>>=
library(dplyr)
library(ggplot2)
@

\section{Simulation}
\label{sec:sim}
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot1", fig.align='center', fig=TRUE, width=14, height=4>>=
load("/Users/ybb/Desktop/Daphnia-article/SF2/SF2.RData")
ggplot() +
  # geom_line(data = all_sims, aes(y = dentadult, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymin, ymax = ymax, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = dentadult), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Non-Parasitize Dyanmics with SF2 Model",
       x = "Day",
       y = "Daphnia dentifera adult density")
@
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=
ggplot() +
  # geom_line(data = all_sims, aes(y = lumadult, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymini, ymax = ymaxi, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = lumadult), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Non-Parasitize Dyanmics with SF2 Model",
       x = "Day",
       y = "Daphnia lumholtzi adult density")
@
\end{subfigure}%
\caption{Plot of Simulation of Non-Parasitize Dyanmics with SF2 Model. The blue shadow implies the possible range from simulation, while the red line shows the real-world data. The various trail represents different buckets in the experiment}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot1", fig.align='center', fig=TRUE, width=14, height=4>>=
load("/Users/ybb/Desktop/Daphnia-article/SIRPF2/SIRPF2.RData")
ggplot() +
  # geom_line(data = all_sims, aes(y = dentadult, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymin, ymax = ymax, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = dentadult), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Parasitize Dyanmics with SIRPF2 Model",
       x = "Day",
       y = "Susceptible Daphnia dentifera adult density")
@
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=
ggplot() +
  # geom_line(data = all_sims, aes(y = lumadult, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymini, ymax = ymaxi, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = lumadult), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Parasitize Dyanmics with SIRPF2 Model",
       x = "Day",
       y = "Susceptible Daphnia lumholtzi adult density")
@
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=
ggplot() +
  # geom_line(data = all_sims, aes(y = luminf, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = iymini, ymax = iymaxi, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = luminf), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Parasitize Dyanmics with SIRPF2 Model",
       x = "Day",
       y = "Infected Daphnia lumholtzi adult density")
@
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=
ggplot() +
  # geom_line(data = all_sims, aes(y = dentinf, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = iymin, ymax = iymax, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = dentinf), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Parasitize Dyanmics with SIRPF2 Model",
       x = "Day",
       y = "Infected Daphnia dentifera adult density")
@
\end{subfigure}%
\caption{Plot of Simulation of Parasitize Dyanmics with SIRPF2 Model. The blue shadow implies the possible range from simulation, while the red line shows the real-world data. The various trail represents different buckets in the experiment}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot1", fig.align='center', fig=TRUE, width=14, height=4>>=
load("/Users/ybb/Desktop/Daphnia-article/SIRPF_invaive/SIRPFI.RData")
ggplot() +
  # geom_line(data = all_sims, aes(y = lumadult, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymin, ymax = ymax, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = lumadult), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Parasitize Dyanmics with SIRPF Model",
       x = "Day",
       y = "Susceptible Daphnia lumholtzi adult density")
@
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=
ggplot() +
  # geom_line(data = all_sims, aes(y = luminf, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymini, ymax = ymaxi, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = luminf), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Parasitize Dyanmics with SIRPF Model",
       x = "Day",
       y = "Infected Daphnia lumholtzi adult density")
@
\end{subfigure}%
\caption{Plot of Simulation of Invasive Parasitize Dyanmics with SIRPF Model. The blue shadow implies the possible range from simulation, while the red line shows the real-world data. The various trail represents different buckets in the experiment}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot1", fig.align='center', fig=TRUE, width=14, height=4>>=
load("/Users/ybb/Desktop/Daphnia-article/SIRPF_native/SIRPFN.RData")
ggplot() +
  # geom_line(data = all_sims, aes(y = dentadult, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymin, ymax = ymax, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = dentadult), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Non-Parasitize Dyanmics with SIRPF Model",
       x = "Day",
       y = "Susceptible Daphnia dentifera adult density")
@
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=
ggplot() +
  # geom_line(data = all_sims, aes(y = dentinf, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymini, ymax = ymaxi, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = dentinf), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Non-Parasitize Dyanmics with SIRPF Model",
       x = "Day",
       y = "Infected Daphnia dentifera adult density")
@
\end{subfigure}%
\caption{Plot of Simulation of Native Parasitize Dyanmics with SIRPF Model. The blue shadow implies the possible range from simulation, while the red line shows the real-world data. The various trail represents different buckets in the experiment}
\end{figure}

\begin{figure}[H]
\centering
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=
load("/Users/ybb/Desktop/Daphnia-article/SF_native/SFN.RData")
ggplot() +
  # geom_line(data = all_sims, aes(y = dentadult, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymin, ymax = ymax, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = dentadult), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Non-Parasitize Dyanmics with SF Model",
       x = "Day",
       y = "Daphnia dentifera adult density")
@
\caption{Plot of Simulation of Native Non-Parasitize Dyanmics with SF Model. The blue shadow implies the possible range from simulation, while the red line shows the real-world data. The various trail represents different buckets in the experiment}
\end{figure}

\begin{figure}[H]
\centering
<<echo=FALSE, fig.cap="Plot2", fig.align='center', fig=TRUE, width=14, height=4>>=
load("/Users/ybb/Desktop/Daphnia-article/SF_native/SFN.RData")
ggplot() +
  # geom_line(data = all_sims, aes(y = dentinf, x = day, group = .id)) +
  geom_line() +
  geom_ribbon(data = max_min_sims, aes(ymin = ymin, ymax = ymax, x = day), fill = "blue", alpha = 0.2) +
  facet_wrap(~unit, scales = "free_y") +
  geom_line(data = data_df, aes(x = day, y = dentadult), col = 'red')+
  theme_minimal() +
  labs(title = "Simulation of Non-Parasitize Dyanmics with SF Model",
       x = "Day",
       y = "Infected Daphnia dentifera adult density")
@
\caption{Plot of Simulation of Invsaive Non-Parasitize Dyanmics with SF Model. The blue shadow implies the possible range from simulation, while the red line shows the real-world data. The various trail represents different buckets in the experiment}
\end{figure}

\newpage
\section{Tables}
<<Setup2, include=FALSE,echo=FALSE,results=hide>>=
library(dplyr)
library(ggplot2)
 myround <- function (x, digits = 1) {
  if (length(digits) > 1) {
    digits <- digits[1]
    warning("Using only digits[1]")
  }
  if (digits < 1) {
    as.character(round(x,digits))
  } else {
    tmp <- sprintf(paste("%.", digits, "f", sep = ""), x)
    zero <- paste0("0.", paste(rep("0", digits), collapse = ""))
    tmp[tmp == paste0("-", zero)] <- zero
    tmp
  }
}

@@

# SF2_ll = load("/Users/ybb/Desktop/Daphnia-article/SF2/SF2_ll.RData")
# SFN_ll = load("/Users/ybb/Desktop/Daphnia-article/SF_native/SFN_ll.RData")
# SFI_ll = load("/Users/ybb/Desktop/Daphnia-article/SF_invasive/SFI_ll.RData")
# SIRPF2_ll = load("/Users/ybb/Desktop/Daphnia-article/SIRPF2/SIRPF2_ll.RData")
# SIRPFN_ll = load("/Users/ybb/Desktop/Daphnia-article/SIRPF_native/SIRPFN_ll.RData")
# SIRPFI_ll = load("/Users/ybb/Desktop/Daphnia-article/SIRPF_invaive/SIRPFI_ll.RData")
load("/Users/ybb/Desktop/Daphnia-article/SIRPF_model_estimate.RData")
@
\renewcommand{\arraystretch}{0.5}
\begin{table}[H]

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[authoryear,numbers]{natbib}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyphenat}
\tolerance=1000
\usepackage{url}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage{hyphenat}
\usepackage{Sweave}
\usepackage{tikz}
\usepackage{float} % For [H] figure placement option
\usetikzlibrary{arrows.meta, shapes.geometric, positioning}
\bibliographystyle{apalike}
\newcommand{\blind}{1}

@@

\if1\blind
{
  \title{\bf Supplement to "Mechanistic models for panel data: analysis of ecological experiments with four interacting species"}
\author{Bo Yang\\Department of Biostatistics, University of Michigan \\
        Jesse Wheeler\\Department of Statistics, University of Michigan \\
        Aaron A. King\\Department of Ecology and Evolutionary Biology \& \\ Center for the Study of Complex Systems, University of Michigan\\
        Edward L. Ionides\\Department of Statistics, University of Michigan}
  \maketitle
} \fi

\if0\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Supplement to "Mechanistic models for panel data: analysis of ecological experiments with four interacting species"}
\end{center}
  \medskip
} \fi

<<Setup, include=FALSE,echo=FALSE,results=hide>>=
 library(plyr)
 library(reshape2)
library(patchwork)
 library(magrittr)
 library(foreach)
 library(readxl)
 library(doParallel)
 registerDoParallel(cores=36)
 library(pomp)
 library(panelPomp)
 library(ggplot2)
 library(gridExtra)

 myround <- function (x, digits = 1) {
  if (length(digits) > 1) {
    digits <- digits[1]
    warning("Using only digits[1]")
  }
  if (digits < 1) {
    as.character(round(x,digits))
  } else {
    tmp <- sprintf(paste("%.", digits, "f", sep = ""), x)
    zero <- paste0("0.", paste(rep("0", digits), collapse = ""))
    tmp[tmp == paste0("-", zero)] <- zero
    tmp
  }
}

@@

 #---------------------------Host Daphnia----------------------------------------------------------------------
 #----------------load data---------------------------------------------------------------
load("data/raw_data.RData")
 #-----------------------------Host with para----------------------------------------------------------------------------
 host_para <- Mesocosm_data[101:180, ]
 host_para <- subset(host_para, select = c(rep, day, dent.adult,dent.inf ))
 host_para <- host_para[80: 1, ]
 #Convert sampling date to natural date. Samples are collected every 5 days after the #first 7 days.
 host_para$day = (host_para$day - 1) * 5 + 7
 host_para_data = list()
 trails = c("K","L","M","N","O","P","Q","S")
 for (i in 1: length(trails)){
   host_para_data[[i]]=subset(host_para, select = c("day", "dent.adult","dent.inf"),
                              host_para$rep == trails[i])
 }

 host_para_plot <- ggplot(host_para,aes(x=day,y=dentadult))+
   geom_line(data=host_para,aes(x=day,y=dent.adult,color = "Susceptible")) +
   geom_line(data=host_para,aes(x=day,y=dent.inf,color = "Infected")) +
   facet_wrap(~rep,scales="free")+labs(y = "Daphnia dentifera adult density")
 #----------------------------------------------------------------------------------------------------------------------

 #-----------------------------Host without para----------------------------------------------------------------------------
 host_nopara <- Mesocosm_data[1:100, ]
 host_nopara <- subset(host_nopara, select = c(rep, day, dent.adult))
 host_nopara <- host_nopara[100: 1, ]
 #Convert sampling date to natural date. Samples are collected every 5 days after the #first 7 days.
 host_nopara$day = (host_nopara$day - 1) * 5 + 7
 host_nopara_data = list()
 trails = c("A","B","C","D","E","F","G","H","I","J")
 for (i in 1: length(trails)){
   host_nopara_data[[i]]=subset(host_nopara, select = c("day", "dent.adult"),
                                host_nopara$rep == trails[i])
 }

 host_nopara_plot <- ggplot(host_nopara,aes(x=day,y=dentadult))+
   geom_line(data=host_nopara,aes(x=day,y=dent.adult)) +
   facet_wrap(~rep,scales="free")+labs(y = "Daphnia dentifera adult density")
 #----------------------------------------------------------------------------------------------------------------------

 #-----------------------------Invasive with para----------------------------------------------------------------------------
 invasive_para <- Mesocosm_data_invasive[101:190, ]
 invasive_para <- subset(invasive_para, select = c(rep, day, lum.adult,lum.adult.inf))
 invasive_para <- invasive_para[90: 1, ]
 #Convert sampling date to natural date. Samples are collected every 5 days after the #first 7 days.
 invasive_para$day = (invasive_para$day - 1) * 5 + 7
 invasive_para_data = list()
 trails = c("L","M","N","O","P","Q","R","S","T")
 for (i in 1: length(trails)){
   invasive_para_data[[i]]=subset(invasive_para, select = c("day", "lum.adult","lum.adult.inf"),
                                  invasive_para$rep == trails[i])
 }

 invasive_para_plot <- ggplot(invasive_para,aes(x=day,y=lumadult))+
   geom_line(data=invasive_para,aes(x=day,y=lum.adult,color = "Susceptible")) +
   geom_line(data=invasive_para,aes(x=day,y=lum.adult.inf,color = "Infected")) +
   facet_wrap(~rep,scales="free")+labs(y = "Daphnia lumholtzi adult density")
 #----------------------------------------------------------------------------------------------------------------------

 #-----------------------------Invasive without para----------------------------------------------------------------------------
 invasive_nopara <- Mesocosm_data_invasive[1:100, ]
 invasive_nopara <- subset(invasive_nopara, select = c(rep, day, lum.adult))
 invasive_nopara <- invasive_nopara[100: 1, ]
 #Convert sampling date to natural date. Samples are collected every 5 days after the #first 7 days.
 invasive_nopara$day = (invasive_nopara$day - 1) * 5 + 7
 invasive_nopara_data = list()
 trails = c("A","B","C","D","E","F","G","H","I","J")
 for (i in 1: length(trails)){
   invasive_nopara_data[[i]]=subset(invasive_nopara, select = c("day", "lum.adult"),
                                    invasive_nopara$rep == trails[i])
 }

 invasive_nopara_plot <- ggplot(invasive_nopara,aes(x=day,y=lumadult))+
   geom_line(data=invasive_nopara,aes(x=day,y=lum.adult)) +
   facet_wrap(~rep,scales="free")+labs(y = "Daphnia lumholtzi adult density")
 #----------------------------------------------------------------------------------------------------------------------

 #-----------------------------Mix with para----------------------------------------------------------------------------
 mixed_para <- Mesocosm_data_mixed[91:170, ]
 mixed_para <- subset(mixed_para, select = c(rep, day, dent.adult,dent.inf,lum.adult,lum.adult.inf))
 mixed_para <- mixed_para[80: 1, ]
 #Convert sampling date to natural date. Samples are collected every 5 days after the #first 7 days.
 mixed_para$day = (mixed_para$day - 1) * 5 + 7
 mixed_para_data = list()
 trails = c("K","L","M","N","O","P","Q","S")
 for (i in 1: length(trails)){
   mixed_para_data[[i]]=subset(mixed_para, select = c("day", "dent.adult","dent.inf","lum.adult","lum.adult.inf"),
                               mixed_para$rep == trails[i])
 }

 mixed_para_plot <- ggplot()+
   geom_line(data=mixed_para,aes(x=day,y=lum.adult,color = "Susceptible lumholtzi"))+
   geom_line(data=mixed_para,aes(x=day,y=lum.adult.inf,color = "Infected lumholtzi")) +
   geom_line(data=mixed_para,aes(x=day,y=dent.adult,color = "Susceptible dentifera")) +
   geom_line(data=mixed_para,aes(x=day,y=dent.inf,color = "Infected dentifera")) +
   facet_wrap(~rep,scales="free")+labs(y = "Daphnia adult density")
 #----------------------------------------------------------------------------------------------------------------------

 #-----------------------------Mix without para----------------------------------------------------------------------------
 mixed_nopara <- Mesocosm_data_mixed[1:90, ]
 mixed_nopara <- subset(mixed_nopara, select = c(rep, day, dent.adult,lum.adult))
 mixed_nopara <- mixed_nopara[90: 1, ]
 #Convert sampling date to natural date. Samples are collected every 5 days after the #first 7 days.
 mixed_nopara$day = (mixed_nopara$day - 1) * 5 + 7
 mixed_nopara_data = list()
 trails = c("A","C","D","E","F","G","H","I","J")
 for (i in 1: length(trails)){
   mixed_nopara_data[[i]]=subset(mixed_nopara, select = c("day", "dent.adult","lum.adult"),
                                 mixed_nopara$rep == trails[i])
 }

 mixed_nopara_plot <- ggplot()+
   geom_line(data=mixed_nopara,aes(x=day,y=lum.adult,color = "Lumholtzi"))+
   geom_line(data=mixed_nopara,aes(x=day,y=dent.adult,color = "Dentifera")) +
   facet_wrap(~rep,scales="free")+labs(y = "Daphnia adult density")
 #----------------------------------------------------------------------------------------------------------------------
 #----------Only lum Model-----------------------------------------------------------------------------------------------
 invasive_nopara_rpro <- Csnippet("
                      double Fbirth, Fpred, Fspl, Ffill, Sgrow, Sdeath, Sspl;
                      double noiB, noiG ;
                      double delta = 0.013; //fraction of volume replaced day-1

                      noiB = rnorm(0, sigB * sqrt(dt));
                      noiG = rnorm(0, sigG * sqrt(dt));

                      //------------F-------------

                      Fbirth = F * (alpha) * (1 - F/kf) * dt + F * noiB;
                      Fpred =  S * F * (Beta * dt);
                      Fspl = F * (delta * dt);
                      Ffill = 0.37 * dt;

                      //------------S--------------
                      Sgrow = S * F * (Theta * dt) + S * noiG;
                      Sdeath = S * (gamma * dt);
                      Sspl = S * (delta * dt);

                      //M is the total Daphnia sample out
                      M += Sspl;
                      F += Fbirth - Fpred + Ffill - Fspl;
                      S += Sgrow - Sdeath  - Sspl;

                      if (S <= 0.0) {
                        S = 0.0;
                        error_count += 1;
                      }
                      if (F <= 0) {
                        F = 0;
                        error_count += 1000;
                      }
                      ")
 invasive_nopara_init = Csnippet("
                     S = 3; //3= 45/15L
                     F = 16.667;
                     M = 0;
                     error_count = 0;
                     ")
 invasive_nopara_dmeas = Csnippet("
                 double delta = 0.013;
                 double tol = 1e-18;

                 if (error_count > 0.0) {
                   lik = log(tol);
                 } else {
                   lik = dpois(lumadult,M,give_log);
                 }
                 ")
 invasive_nopara_rmeas = Csnippet("
                 //double delta = 0.013;
                 lumadult = rpois(M);
                 ")
 invasive_nopara_pt <- parameter_trans(
   log = c("alpha", "Beta", "Theta", "gamma", "sigB", "sigG", "kf")
 )
 invasive_nopara_pomplist=list()
 #Not sure about the consumption rate of alga
 invasive_nopara_parameters = c(1, 0.0002500899,40,2, 10,0.2496332878,0.3)
 names(invasive_nopara_parameters) =  c("alpha","Beta", "gamma", "Theta","kf","sigB","sigG")

 for (i in 1:10){
   colnames(invasive_nopara_data[[i]]) <- c('day', 'lumadult')
   pomp(data = invasive_nopara_data[[i]],
        times = "day",
        t0=1,
        rprocess=euler(invasive_nopara_rpro,delta.t=1/4),
        rinit = invasive_nopara_init,
        dmeasure = invasive_nopara_dmeas,
        rmeasure = invasive_nopara_rmeas,
        partrans = invasive_nopara_pt,
        obsnames = "lumadult",
        accumvars = c("error_count","M"),
        paramnames = c("alpha", "Beta", "Theta", "gamma", "sigB", "sigG", "kf"),
        statenames = c("S", "error_count", "F","M")
   ) -> invasive_nopara_pomplist[[i]]
   coef(invasive_nopara_pomplist[[i]])=invasive_nopara_parameters
 }
 names(invasive_nopara_pomplist)=paste("u", 1:10,sep = "")

 invasive_nopara_shared_parameter =        c(0.0002500899 ,40   ,10    ,0.2496332878,  1, 2)
 names(invasive_nopara_shared_parameter) = c("Beta","gamma","kf","sigB","alpha", "Theta")

 invasive_nopara_specific_mat = matrix(data = c(rep(0.3, 10)),
                                       nrow = 1, nc = 10, byrow = T,
                                       dim = list(rownames = c("sigG"),
                                                  colnames=c("u1","u2","u3","u4","u5", "u6","u7","u8","u9","u10")))

 invasive_nopara_panelfood = panelPomp(invasive_nopara_pomplist, shared=invasive_nopara_shared_parameter,specific = invasive_nopara_specific_mat)

 #----------------------------------------------------------------------------------------------------------------------

 #----------Only dent Model-----------------------------------------------------------------------------------------------
 host_nopara_rpro <- Csnippet("
                      double Fbirth, Fpred, Fspl, Ffill, Sgrow, Sdeath, Sspl;
                      double noiB, noiG ;
                      double delta = 0.013; //fraction of volume replaced day-1

                      noiB = rnorm(0, sigB * sqrt(dt));
                      noiG = rnorm(0, sigG * sqrt(dt));

                      //------------F-------------

                      Fbirth = F * (alpha) * (1 - F/kf) * dt + F * noiB;
                      Fpred =  S * F * (Beta * dt);
                      Fspl = F * (delta * dt);
                      Ffill = 0.37 * dt;

                      //------------S--------------
                      Sgrow = S * F * (Theta * dt) + S * noiG;
                      Sdeath = S * (gamma * dt);
                      Sspl = S * (delta * dt);

                      //M is the total Daphnia sample out
                      M += Sspl;
                      F += Fbirth - Fpred + Ffill - Fspl;
                      S += Sgrow - Sdeath  - Sspl;

                      if (S <= 0.0) {
                        S = 0.0;
                        error_count += 1;
                      }
                      if (F <= 0) {
                        F = 0;
                        error_count += 1000;
                      }
                      ")
 # Initial state. Assume t0 = day 4
 host_nopara_init = Csnippet("
                     S = 3; //3= 45/15L
                     F = 16.667;
                     M = 0;
                     error_count = 0;
                     ")

 host_nopara_dmeas = Csnippet("
                 double delta = 0.013;
                 double tol = 1e-18;

                 if (error_count > 0.0) {
                   lik = log(tol);
                 } else {
                   lik = dpois(dentadult,M,give_log);
                 }
                 ")

 host_nopara_rmeas = Csnippet("
                 //double delta = 0.013;
                 dentadult = rpois(M);
                 ")

 host_nopara_pt <- parameter_trans(
   log = c("alpha", "Beta", "Theta", "gamma", "sigB", "sigG", "kf")
 )

 host_nopara_pomplist=list()

 #Not sure about the consumption rate of alga
 host_nopara_parameters = c(0.5, 0.0005,0.03,0.1, 8,0.6,0.3)
 names(host_nopara_parameters) =  c("alpha","Beta", "gamma", "Theta","kf","sigB","sigG")

 for (i in 1:10){
   colnames(host_nopara_data[[i]]) <- c('day', 'dentadult')
   pomp(data = host_nopara_data[[i]],
        times = "day",
        t0=1,
        rprocess=euler(host_nopara_rpro,delta.t=1/4),
        rinit = host_nopara_init,
        dmeasure = host_nopara_dmeas,
        rmeasure = host_nopara_rmeas,
        partrans = host_nopara_pt,
        obsnames = "dentadult",
        accumvars = c("error_count","M"),
        paramnames = c("alpha", "Beta", "Theta", "gamma", "sigB", "sigG", "kf"),
        statenames = c("S", "error_count", "F","M")
   ) -> host_nopara_pomplist[[i]]
   coef(host_nopara_pomplist[[i]])=host_nopara_parameters
 }
 names(host_nopara_pomplist)=paste("u", 1:10,sep = "")

 host_nopara_shared_parameter =        c(7.773061e-05  ,2.052644e-01   ,1.790036    ,6.940058e-03  ,1.170719e-01, 0.15)
 names(host_nopara_shared_parameter) = c("Beta","gamma","kf","sigB","alpha", "Theta")

 host_nopara_specific_mat = matrix(data = c(rep(0.3, 10)),
                                   nrow = 1, nc = 10, byrow = T,
                                   dim = list(rownames = c("sigG"),
                                              colnames=c("u1","u2","u3","u4","u5", "u6","u7","u8","u9","u10")))

 host_nopara_panelfood = panelPomp(host_nopara_pomplist, shared=host_nopara_shared_parameter,specific = host_nopara_specific_mat)

 #----------------------------------------------------------------------------------------------------------------------

 #----------dent par Model----------------------------------------------
 dent_par_rpro <- Csnippet("
                      double S_term, I_term, F_term, P_term;
                      double noiS, noiI, noiF, noiP;
                      double delta = 0.013; //fraction of volume replaced day-1

                      noiS = rnorm(0, sigS * sqrt(dt));
                      noiI = rnorm(0, sigI * sqrt(dt));
                      noiF = rnorm(0, sigF * sqrt(dt));
                      noiP = rnorm(0, sigP * sqrt(dt));

                      //------------s-------------
                      //Model without death part
                      S_term = r  * F * (S + zeta * I) * dt - theta_S * S * dt - prob * f_S * S * P * dt - delta * S * dt + S * noiS;

                      //------------I--------------

                      I_term = prob * f_S * S * P * dt - theta_I * I *dt - delta * I * dt + I * noiI;

                      //-----------F---------------

                      F_term = alpha * F * (1 - F/K_F) * dt + F * noiF - gamma * F * (S + zeta * I) * dt - delta * F * dt + 0.37 * dt;

                      //----------P---------------

                      P_term = beta * theta_I * I * dt - f_S * S * P * dt - f_I * I * P * dt - theta_P * P * dt - delta * P * dt + P * noiP;

                      //T_D and T_I are the S and I Daphnia sample out
                      F += F_term;
                      S += S_term;
                      I += I_term;
                      P += P_term;

                      T_D += delta * S * dt;
                      T_I += delta * I * dt;

                      //Trace time

                     if (t - 4.0 < 0.000000001 && t - 4.0 > -0.000000001){
                      //Initial statement
                        P += 25;
                      }

                      if (S < 0.0) {
                        S = 0.0;
                        error_count += 1;
                      }
                      if (F < 0) {
                        F = 0;
                        error_count += 1000;
                      }
                      if (I < 0) {
                        I = 0;
                        error_count += 0.001;
                      }
                      if (P < 0 && t > 3.9) {
                        P = 0;
                        error_count += 0.000001;
                      }

                      ")

 # Initial state. Assume t0 = day 4
 dent_par_init = Csnippet("
                     S = 3; //3= 45/15L
                     F = 16.667;
                     T_D = 0;
                     T_I = 0;
                     I = 0;

                     error_count = 0.0;

                     //add 25 P at day 4
                     P = 0;
                     ")

 dent_par_dmeas = Csnippet("
                 double tol = 1e-18;

                  if (error_count > 0.0) {
                   lik = -100;
                  }
                 else{
                    if(give_log){
                    lik  = dnbinom_mu(dentadult,k_S,T_D,give_log) +  dnbinom_mu(dentinf,k_I,T_I,give_log);
                    }
                    else{
                    lik  = dnbinom_mu(dentadult,k_S,T_D,give_log) *  dnbinom_mu(dentinf,k_I,T_I,give_log);
                    }
                      }

                 ")

 dent_par_rmeas = Csnippet("
                 dentadult = rnbinom_mu(k_S,T_D);
                 dentinf = rnbinom_mu(k_I,T_I);
                 ")

 dent_par_pt <- parameter_trans(
   log = c("alpha", "beta", "gamma", "sigS", "sigI", "sigF","sigP","K_F","f_S","theta_P","r", "f_I","k_S","k_I"),
   logit = c('prob',"zeta","theta_S","theta_I")
 )

 dent_par_pomplist=list()

 dent_par_parameters =         c(0.16,   2.8   ,   0.00011,   0.1,    0.1,   0.7,  0.2,     0.01,     0.8,     2.3,  0.001,   0.2,      0.1,  0.06 ,  0.7,   0.003,10,10)
 names(dent_par_parameters) =  c("alpha", "beta",  "gamma", "sigS", "sigI", "sigF","sigP","theta_S","theta_I","K_F", "f_S",  "theta_P", "r", "zeta", "prob", "f_I","k_S","k_I")

 for (i in 1:8){
   colnames(host_para_data[[i]]) <- c('day', 'dentadult', 'dentinf')
   pomp(data = host_para_data[[i]],
        times = "day",
        t0=1,
        rprocess=euler(dent_par_rpro,delta.t=1/4),
        rinit = dent_par_init,
        dmeasure = dent_par_dmeas,
        rmeasure = dent_par_rmeas,
        partrans = dent_par_pt,
        obsnames = c("dentadult", "dentinf"),
        accumvars = c("error_count","T_D","T_I"),
        paramnames = c("alpha", "beta",  "gamma", "sigS", "sigI", "sigF","sigP","theta_S","theta_I","K_F", "f_S",  "theta_P", "r", "zeta", "prob", "f_I","k_S","k_I"),
        statenames = c("S",  "I", "error_count", "F", "T_D","T_I","P")
   ) -> dent_par_pomplist[[i]]
   coef(dent_par_pomplist[[i]])=dent_par_parameters
 }
 names(dent_par_pomplist)=paste("u", 1:8,sep = "")
